---
title: "WMA_pbmc"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analyzing each dataset 
```{r}
library(DT)
library(UpSetR)

path_with_WMA <- '/Users/korshe/Documents/Data_Groningen/pbmc_5ds/'
dataset_ids <- c('stemi_v2','stemi_v3','v2_1m','v3_1m', 'ng')

tab_eqtls <- read.table(paste(path_with_WMA,'Sample.size._tab.tsv',sep=''), sep='\t', header=T)
tab <- tab_eqtls
for (dataset_id in dataset_ids){
#tab<- tab %>% group_by(bulk.feature_id) %>%   arrange(cFDR_empirical_feature_p_value)
tab <- tab[order(tab[,paste0('p_value_', dataset_id )], decreasing = F),]
tab_bh = multtest::mt.rawp2adjp(c("BH","Bonferroni"),rawp = tab[,paste0('p_value_', dataset_id )])$adjp
tab[,paste0('BH_', dataset_id )] <- tab_bh[,2]
tab[,paste0('Bonf_', dataset_id )] <- tab_bh[,3]
}


UpSetR::upset(fromList(list(NG= tab[tab$BH_ng <0.05, ]$snp_gene, 
                            STEMI_v2 = tab[tab$BH_stemi_v2 <0.05, ]$snp_gene,
                            STEMI_v3 = tab[tab$BH_stemi_v3 <0.05, ]$snp_gene,
                            V2_1M = tab[tab$BH_v2_1m <0.05, ]$snp_gene,
                            V3_1M = tab[tab$BH_v3_1m <0.05, ]$snp_gene
                            # ,
                            # WMA_SS = tab[tab$BH_ZW_ss <0.05, ]$snp_gene,
                            # WMA_SE = tab[tab$BH_ZW_SE <0.05, ]$snp_gene
                            )), 
              set_size.show = T, order.by = 'freq', nintersects = 60,nsets = 20,sets.x.label = 'BH eQTLs')

UpSetR::upset(fromList(list(NG= tab[tab$BH_ng <0.05, ]$feature_id, 
                            STEMI_v2 = tab[tab$BH_stemi_v2 <0.05, ]$feature_id,
                            STEMI_v3 = tab[tab$BH_stemi_v3 <0.05, ]$feature_id,
                            V2_1M = tab[tab$BH_v2_1m <0.05, ]$feature_id,
                            V3_1M = tab[tab$BH_v3_1m <0.05, ]$feature_id
                            # ,
                            # WMA_SS = tab[tab$BH_ZW_ss <0.05, ]$feature_id,
                            # WMA_SE = tab[tab$BH_ZW_SE <0.05, ]$feature_id
                            )), 
              set_size.show = T, order.by = 'freq', nintersects = 60,nsets = 20,sets.x.label = 'BH eGenes')

UpSetR::upset(fromList(list(NG= tab[tab$Bonf_ng <0.05, ]$snp_gene, 
                            STEMI_v2 = tab[tab$Bonf_stemi_v2 <0.05, ]$snp_gene,
                            STEMI_v3 = tab[tab$Bonf_stemi_v3 <0.05, ]$snp_gene,
                            V2_1M = tab[tab$Bonf_v2_1m <0.05, ]$snp_gene,
                            V3_1M = tab[tab$Bonf_v3_1m <0.05, ]$snp_gene
                            # ,
                            # WMA_SS = tab[tab$Bonf_ZW_ss <0.05, ]$snp_gene,
                            # WMA_SE = tab[tab$Bonf_ZW_SE <0.05, ]$snp_gene
                            )), 
              set_size.show = T, order.by = 'freq', nintersects = 60,nsets = 20,sets.x.label = 'Bonf eQTLs')

UpSetR::upset(fromList(list(NG= tab[tab$Bonf_ng <0.05, ]$feature_id, 
                            STEMI_v2 = tab[tab$Bonf_stemi_v2 <0.05, ]$feature_id,
                            STEMI_v3 = tab[tab$Bonf_stemi_v3 <0.05, ]$feature_id,
                            V2_1M = tab[tab$Bonf_v2_1m <0.05, ]$feature_id,
                            V3_1M = tab[tab$Bonf_v3_1m <0.05, ]$feature_id
                            # ,
                            # WMA_SS = tab[tab$Bonf_ZW_ss <0.05, ]$feature_id,
                            # WMA_SE = tab[tab$Bonf_ZW_SE <0.05, ]$feature_id
                            )), 
              set_size.show = T, order.by = 'freq', nintersects = 60,nsets = 20,sets.x.label = 'Bonf eGenes')


```
## Expression parameters 
```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(gridExtra)
param = 'mean_log.donor'
summary_stat_filteres <- tab
get_plot_for_values <- function(summary_stat_filteres,param){
  #summary_stat_filteres <- summary_stat_filteres[1:500,]
  param_cols <- colnames(summary_stat_filteres)[grep(param, colnames(summary_stat_filteres))]
  summary_stat_filteres_par <- summary_stat_filteres %>%  select(one_of(param_cols), snp_gene)
  
  summary_stat_filteres_par <- summary_stat_filteres_par[sample(nrow(summary_stat_filteres_par), 1500), ] #sample(summary_stat_filteres_par, 1000)
  colnames(summary_stat_filteres_par) <-  gsub(param, "", colnames(summary_stat_filteres_par))
  colnames(summary_stat_filteres_par) <-  gsub("_", "", colnames(summary_stat_filteres_par))
  
  colnames(summary_stat_filteres_par)[ colnames(summary_stat_filteres_par) == 'stemiv2'] <- 'van_Blokland_v2'
  colnames(summary_stat_filteres_par)[ colnames(summary_stat_filteres_par) == 'stemiv3'] <- 'van_Blokland_v3'
  colnames(summary_stat_filteres_par)[ colnames(summary_stat_filteres_par) == 'ng'] <- 'van_der_Wijst_v2'
  colnames(summary_stat_filteres_par)[ colnames(summary_stat_filteres_par) == 'v21m'] <- 'Oelen_v2'
  colnames(summary_stat_filteres_par)[ colnames(summary_stat_filteres_par) == 'v31m'] <- 'Oelen_v3'
  
  summary_stat_filteres_par <- summary_stat_filteres_par[order(as.numeric(summary_stat_filteres_par$van_der_Wijst_v2)), ]
  summary_stat_filteres_par$gene <- 1:length(summary_stat_filteres_par$snpgene)
  data_long <- gather(summary_stat_filteres_par, condition, measurement, 1:5, factor_key=TRUE)
  data_long$measurement <- as.numeric(data_long$measurement)
  print(param)
  #data_long <- data_long[order(data_long$measurement),]
  plot1<- 
    ggplot(data = data_long, aes(x = gene, y = measurement, color = condition)) +  geom_line()  +theme_light()  + 
    scale_x_continuous(name="Gene id")
  
  
  plot2<-ggplot(data = data_long,
                mapping = aes(x = gene, y = measurement, color = condition)) +theme_light() +
    geom_line() +
    facet_grid(rows = vars(condition)) + ggtitle(param) 


  plot3 <- ggplot(data_long, aes(x = measurement, color = condition)) + theme_light() + geom_density(alpha=.3) + 
  scale_x_continuous(name=param, limits=c(0, 6))
  # grid.arrange(plot1,plot2, plot3, ncol = 3)
  # grid.arrange(plot1, plot3, ncol = 2)
  grid.arrange(plot3, plot2, ncol = 2)
  
  #grid.arrange(plot1p,plot2p)
}

```

```{r, fig.height=2.5}
get_plot_for_values(summary_stat_filteres,param='mean.donor')
```
```{r, fig.height=2.5}
get_plot_for_values(summary_stat_filteres,param='mean.cell')
```
```{r, fig.height=2.5}
get_plot_for_values(summary_stat_filteres,param='sd.donor')
```
```{r, fig.height=2.5}
get_plot_for_values(summary_stat_filteres,param='sd.cell')

```
```{r, fig.height=2.5}
get_plot_for_values(summary_stat_filteres,param='sd_prop')
```


# WMA efficiency estimate 5ds
```{r}
weights <- read.table(paste(path_with_WMA,'list_of_weighting_ids.tsv',sep=''), sep='\t', header=T)
weights$x
```

```{r}
dataset_characteristics <- read.table(paste(path_with_WMA,'PBMC_dataset_specifications.csv',sep=''), sep=',', header=T)
datatable(dataset_characteristics,extensions = "Buttons", 
            options = list(paging = TRUE,
                           scrollX=TRUE, 
                           searching = TRUE,
                           ordering = TRUE,
                           dom = 'Bfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf') ))
```

# Weights and weighting characteristics 

Check what  it the most optimal weighting using n eQTLs BH-corrected 

```{r}
library(DT)
path_with_WMA <- '/Users/korshe/Documents/Data_Groningen/pbmc_5ds/'

BH <- read.table(paste(path_with_WMA,'BH','.tsv',sep=''), sep='\t', header=T)
BH <- BH[order(BH$eQTLs),]
BH <- BH[,c(10,11,1:9)]
DT::datatable(BH,extensions = "Buttons", 
            options = list(paging = TRUE,
                           scrollX=TRUE, 
                           searching = TRUE,
                           ordering = TRUE,
                           dom = 'Bfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf') ))
```

Check what  it the most optimal weighting using n eQTLs Bonferroni-corrected 

```{r}
Bonf <- read.table(paste(path_with_WMA,'Bonf','.tsv',sep=''), sep='\t', header=T)
Bonf <- Bonf[order(Bonf$eQTLs),]
Bonf <- Bonf[,c(10,11,1:9)]
DT::datatable(Bonf,extensions = "Buttons", 
            options = list(paging = TRUE,
                           scrollX=TRUE, 
                           searching = TRUE,
                           ordering = TRUE,
                           dom = 'Bfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf') ))
```

```{r}
library(viridis)
tab <- tab[complete.cases(tab),]
get_density <- function(x, y, ...) {
  dens <- MASS::kde2d(x, y, ...)
  ix <- findInterval(x, dens$x)
  iy <- findInterval(y, dens$y)
  ii <- cbind(ix, iy)
  return(dens$z[ii])
}

tab$density <- get_density(tab$ZW_weight_ss, tab$OverallZScore.eqtlgen_ng, n = 105)

ggplot(tab) + geom_point(aes(tab$ZW_weight_ss, tab$OverallZScore.eqtlgen_ng, color = density))  + theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "grey")) +  labs(y = "ZScore from eQTLGen", x = "Weighted ZScore (SS)")  +  scale_color_viridis()

ggplot(tab) + geom_point(aes(tab$ZW_weight_SE, tab$OverallZScore.eqtlgen_ng, color = density))  + theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "grey")) +  labs(y = "ZScore from eQTLGen", x = "Weighted ZScore (SE)")  +  scale_color_viridis()
```

# WMA estimate for pairwise weighting

```{r}
path_wma_pairwise <- '/Users/korshe/Documents/Data_Groningen/pbmc_pairwise_2022/ALL/'
datset_combination = 'ng_vs_stemi_v2'

tab_prep <- function(path_wma_pairwise, datset_combination){
ng_stemi_v2 <- read.table(paste(path_wma_pairwise,'ALL_',datset_combination,'.tsv',sep=''), sep='\t', header=T)
ng_stemi_v2= ng_stemi_v2[order(ng_stemi_v2$Bonf_genes,ng_stemi_v2$Bonf_TP,decreasing = c(T,T)),]
ng_stemi_v2["rank_genes"] = c(1:nrow(ng_stemi_v2))
ng_stemi_v2$weight <- paste(ng_stemi_v2$ss, gsub('[0-9]+', '', rownames(ng_stemi_v2) ), sep='_')
return(ng_stemi_v2)
}
```
## Between chemistries 

```{r}
ng_vs_stemi_v2 <- tab_prep(path_wma_pairwise, datset_combination)

datatable(ng_vs_stemi_v2[,c(1:2,4,6, 10,11)],extensions = "Buttons", 
            options = list(buttons = c('copy', 'csv', 'excel', 'pdf') ))

```

```{r}
ng_vs_v2_1m <- tab_prep(path_wma_pairwise, datset_combination='ng_vs_v2_1m')

datatable(ng_vs_v2_1m[,c(1:2,4,6, 10,11)],extensions = "Buttons", 
            options = list(buttons = c('copy', 'csv', 'excel', 'pdf') ))
```

```{r}
stemi_v3_vs_v3_1m <- tab_prep(path_wma_pairwise, datset_combination='stemi_v3_vs_v3_1m')

datatable(stemi_v3_vs_v3_1m[,c(1:2,4,6, 10,11)],extensions = "Buttons", 
            options = list(buttons = c('copy', 'csv', 'excel', 'pdf') ))
```

```{r}
#library(matrixStats)
inter_chemistries_agr_rank <- merge(ng_vs_stemi_v2[,c('weight','rank_genes') ],ng_vs_v2_1m[,c('weight','rank_genes')],by= 'weight')
inter_chemistries_agr_rank <- merge(inter_chemistries_agr_rank,stemi_v3_vs_v3_1m[,c('weight','rank_genes')],by= 'weight')
inter_chemistries_agr_rank$weight <- gsub('.tsv', '', inter_chemistries_agr_rank$weight )
rownames(inter_chemistries_agr_rank) <- inter_chemistries_agr_rank$weight
inter_chemistries_agr_rank$weight <- NULL
inter_chemistries_agr_rank$agregated_rank <- rowSums(inter_chemistries_agr_rank)
inter_chemistries_agr_rank <- inter_chemistries_agr_rank[order(inter_chemistries_agr_rank$agregated_rank),]

datatable(inter_chemistries_agr_rank,extensions = "Buttons", 
            options = list(paging = TRUE,
                           scrollX=TRUE, 
                           searching = TRUE,
                           ordering = TRUE,
                           dom = 'Bfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf') ))
```

## Between chemistries 

```{r}
stemi_v3_vs_stemi_v2 <- tab_prep(path_wma_pairwise, datset_combination='stemi_v3_vs_stemi_v2')

datatable(stemi_v3_vs_stemi_v2[,c(1:2,4,6, 10,11)],extensions = "Buttons", 
            options = list(buttons = c('copy', 'csv', 'excel', 'pdf') ))
```

```{r}
ng_vs_v3_1m <- tab_prep(path_wma_pairwise, datset_combination='ng_vs_v3_1m')

datatable(ng_vs_v3_1m[,c(1:2,4,6, 10,11)],extensions = "Buttons", 
            options = list(buttons = c('copy', 'csv', 'excel', 'pdf') ))
```

```{r}
v3_1m_vs_v2_1m <- tab_prep(path_wma_pairwise, datset_combination='v3_1m_vs_v2_1m')

datatable(v3_1m_vs_v2_1m[,c(1:2,4,6, 10,11)],extensions = "Buttons", 
            options = list(buttons = c('copy', 'csv', 'excel', 'pdf') ))
```

### Getting aggregated rank 

```{r}
#library(matrixStats)
between_chemistries_agr_rank <- merge(v3_1m_vs_v2_1m[,c('weight','rank_genes') ],ng_vs_v3_1m[,c('weight','rank_genes')],by= 'weight')
between_chemistries_agr_rank <- merge(between_chemistries_agr_rank,stemi_v3_vs_stemi_v2[,c('weight','rank_genes')],by= 'weight')
between_chemistries_agr_rank$weight <- gsub('.tsv', '', between_chemistries_agr_rank$weight )
rownames(between_chemistries_agr_rank) <- between_chemistries_agr_rank$weight
between_chemistries_agr_rank$weight <- NULL
between_chemistries_agr_rank$agregated_rank <- rowSums(between_chemistries_agr_rank)
between_chemistries_agr_rank <- between_chemistries_agr_rank[order(between_chemistries_agr_rank$agregated_rank),]

datatable(between_chemistries_agr_rank,extensions = "Buttons", 
            options = list(paging = TRUE,
                           scrollX=TRUE, 
                           searching = TRUE,
                           ordering = TRUE,
                           dom = 'Bfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf') ))
```

# Grid search
## functions
```{r}
dataset_combination <- 'ng_vs_stemi_v2'
grid_path <- '/Users/korshe/Documents/Data_Groningen/pbmc_pairwise_2022/grid_search/'

heatmap_fun <- function(grid_path,dataset_combination){
grid_tab <- read.table(paste(grid_path,'Grid_summary_',dataset_combination,'.tsv',sep=''), sep='\t', header=T)
dim(grid_tab)
grid_tab$param <- NULL
grid_tab <- grid_tab[order(grid_tab$grid),]
grid_tab <- grid_tab[!duplicated(grid_tab$grid),]
rownames(grid_tab) <- paste(grid_tab$grid)
grid_tab$grid <- NULL
nba_heatmap <- heatmap(t(as.matrix(grid_tab)),Colv = NA, Rowv = NA, scale="column", main = paste(dataset_combination, 'Grid search'))
}

```

```{r}
 library(knitr)

show_most_optimal_weight <- function(grid_path,dataset_combination){
grid_tab <- read.table(paste(grid_path,'Grid_summary_',dataset_combination,'.tsv',sep=''), sep='\t', header=T)
grid_tab$param <- NULL
grid_tab <- grid_tab[order(grid_tab$SS, decreasing = T),]
SS_grid <- grid_tab[1:5, c('grid','SS')]
#grid_tab <- grid_tab[grid_tab$grid < 15,]
grid_tab_long <- gather(grid_tab, weight, neQTLs, 1:38, factor_key=TRUE)
grid_tab_long <- grid_tab_long[order(grid_tab_long$neQTLs, decreasing = T),]
head(grid_tab_long)
max(grid_tab)
# knitr::kable(SS_grid,  caption = paste(dataset_combination, 'SS-based WMA'))
# knitr::kable(grid_tab_long[1:20,],  caption = paste(dataset_combination, 'Top grid with other params'))
 t1 <- head(SS_grid)
 t2 <- head(grid_tab_long[1:20,])
 print(kable(t1),caption = paste(dataset_combination, 'SS-based WMA'))
 print(kable(t2), caption = paste(dataset_combination, 'Top grid with other parameters'))
}

#show_most_optimal_weight(grid_path, dataset_combination)
```

```{r}
library(dplyr)
library(ggplot2)
library(tidyr)

line_fun <- function(grid_path,dataset_combination){
grid_tab <- read.table(paste(grid_path,'Grid_summary_',dataset_combination,'.tsv',sep=''), sep='\t', header=T)
dim(grid_tab)
grid_tab$param <- NULL
grid_tab <- grid_tab[order(grid_tab$grid),]
grid_tab <- grid_tab[!duplicated(grid_tab$grid),]
rownames(grid_tab) <- paste(grid_tab$grid)
# removing columns which have avr score less than SS 

grid_tab_means <- as.data.frame(colMeans(grid_tab))
colnames(grid_tab_means) <- 'mean'
grid_tab_means$weight <- rownames(grid_tab_means)
grid_tab_means_less_SS<- grid_tab_means[grid_tab_means$mean > grid_tab_means[1,1],'weight']
grid_tab_means <- grid_tab_means[order(grid_tab_means$mean, decreasing = T),]
grid_tab <- grid_tab[grid_tab$grid < 10,]
grid_tab_subset_top_5 <- grid_tab[,colnames(grid_tab) %in% c(grid_tab_means$weight[1:5],'SS', 'grid')]
dim(grid_tab_subset_top_5)

grid_tab_long <- gather(grid_tab_subset_top_5, weight, neQTLs, 1:6, factor_key=TRUE)

grid_tab_long %>%  ggplot(aes(x=grid, y=neQTLs, group=weight, color=weight)) + geom_line() + theme_light() + ggtitle(paste(dataset_combination, "top 5 weights and Sample size"))
}

```
## results


```{r, fig.height=4}
dataset_combination = 'ng_vs_stemi_v2'
heatmap_fun(grid_path,dataset_combination)
show_most_optimal_weight(grid_path,dataset_combination)
```

```{r, fig.height=3}
line_fun(grid_path,dataset_combination)
```


```{r, fig.height=4}
dataset_combination = 'ng_vs_stemi_v3'
heatmap_fun(grid_path,dataset_combination)
show_most_optimal_weight(grid_path,dataset_combination)
```

```{r, fig.height=3}
line_fun(grid_path,dataset_combination)
```


```{r, fig.height=4}
dataset_combination = 'ng_vs_v2_1m'
heatmap_fun(grid_path,dataset_combination)
show_most_optimal_weight(grid_path,dataset_combination)
```

```{r, fig.height=3}
line_fun(grid_path,dataset_combination)
```


```{r, fig.height=4}
dataset_combination = 'ng_vs_v3_1m'
heatmap_fun(grid_path,dataset_combination)
show_most_optimal_weight(grid_path,dataset_combination)
```

```{r, fig.height=3}
line_fun(grid_path,dataset_combination)

```

```{r, fig.height=4}
dataset_combination = 'v3_1m_vs_stemi_v2'
heatmap_fun(grid_path,dataset_combination)
show_most_optimal_weight(grid_path,dataset_combination)
```

```{r, fig.height=4}
dataset_combination = 'v3_1m_vs_stemi_v3'
heatmap_fun(grid_path,dataset_combination)
show_most_optimal_weight(grid_path,dataset_combination)
```

```{r, fig.height=3}
line_fun(grid_path,dataset_combination)
```

```{r, fig.height=4}
dataset_combination = 'v3_1m_vs_v2_1m'
heatmap_fun(grid_path,dataset_combination)
show_most_optimal_weight(grid_path,dataset_combination)
```

```{r, fig.height=3}
line_fun(grid_path,dataset_combination)
```


# WMA on subset of genes 

For genes with high GC top three optimal WMA weights are XXX, XXX, XXX.
```{r}
path_summary <- '/Users/korshe/Documents/Data_Groningen/pbmc_pairwise_2022/subset_of_genes/'
dataset_combination <- 'v2_1m_vs_v3_1m'
parameter <- 'length'

top_param_high <- function(path_summary, dataset_combination, parameter){
  high_tab <- read.table(paste(path_summary,'1_Total_summary_',dataset_combination,'Sample.size.',parameter,'.donor_HIGHT.tsv',sep=''), sep='\t', header=T)
  high_tab_t <- as.data.frame(t(high_tab))
  colnames(high_tab_t) <- high_tab_t[1,]
  high_tab_t<- high_tab_t[-1,]
  
  high_tab_t <- high_tab_t[order(high_tab_t$BH_SS_eQTLs, decreasing = T),]
high_tab_t_3 <- high_tab_t[1:5,c('BH_SS_genes','BH_SS_eQTLs','cor_SS_all','cor_SS_sign')]
high_tab_t_SS <- high_tab_t[rownames(high_tab_t)=="Sample.size.",c('BH_SS_genes','BH_SS_eQTLs','cor_SS_all','cor_SS_sign')]
high_tab_t_SE <- high_tab_t[rownames(high_tab_t)=="Sample.size.",c('BH_SE_genes','BH_SE_eQTLs','cor_SE_all','cor_SE_sign')]
rownames(high_tab_t_SE) <- "SE"
colnames(high_tab_t_SE) <-c('BH_SS_genes','BH_SS_eQTLs','cor_SS_all','cor_SS_sign')
high_tab_t_3 <- rbind(high_tab_t_3,high_tab_t_SS)
high_tab_t_3 <- rbind(high_tab_t_3,high_tab_t_SE)
knitr::kable(high_tab_t_3,  caption = paste(dataset_combination, 'WMA of subset of genes with high', parameter))
}
top_param_low <- function(path_summary, dataset_combination, parameter){
  high_tab <- read.table(paste(path_summary,'1_Total_summary_',dataset_combination,'Sample.size.',parameter,'.donor_LOW.tsv',sep=''), sep='\t', header=T)
  high_tab_t <- as.data.frame(t(high_tab))
  colnames(high_tab_t) <- high_tab_t[1,]
  high_tab_t<- high_tab_t[-1,]
  
  high_tab_t <- high_tab_t[order(high_tab_t$BH_SS_eQTLs, decreasing = T),]
high_tab_t_3 <- high_tab_t[1:5,c('BH_SS_genes','BH_SS_eQTLs','cor_SS_all','cor_SS_sign')]
high_tab_t_SS <- high_tab_t[rownames(high_tab_t)=="Sample.size.",c('BH_SS_genes','BH_SS_eQTLs','cor_SS_all','cor_SS_sign')]
high_tab_t_SE <- high_tab_t[rownames(high_tab_t)=="Sample.size.",c('BH_SE_genes','BH_SE_eQTLs','cor_SE_all','cor_SE_sign')]
rownames(high_tab_t_SE) <- "SE"
colnames(high_tab_t_SE) <-c('BH_SS_genes','BH_SS_eQTLs','cor_SS_all','cor_SS_sign')
high_tab_t_3 <- rbind(high_tab_t_3,high_tab_t_SS)
high_tab_t_3 <- rbind(high_tab_t_3,high_tab_t_SE)
knitr::kable(high_tab_t_3,  caption = paste(dataset_combination, 'WMA of subset of genes with low', parameter))
}
```

## 1M v2 & v3
```{r}
top_param_high(path_summary, dataset_combination, parameter='length')
top_param_low(path_summary, dataset_combination, parameter='length')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='gc')
top_param_low(path_summary, dataset_combination, parameter='gc')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='mean')
top_param_low(path_summary, dataset_combination, parameter='mean')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='sd')
top_param_low(path_summary, dataset_combination, parameter='sd')
```

## NG v2 & 1M v3
```{r}
dataset_combination ='ng_vs_v3_1m'
top_param_high(path_summary, dataset_combination, parameter='length')
top_param_low(path_summary, dataset_combination, parameter='length')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='gc')
top_param_low(path_summary, dataset_combination, parameter='gc')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='mean')
top_param_low(path_summary, dataset_combination, parameter='mean')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='sd')
top_param_low(path_summary, dataset_combination, parameter='sd')
```

```{r}
#parameters <- c('gc','length','mean','sd')
```


## NG v2 & STEMI v2
```{r}
dataset_combination ='ng_vs_stemi_v2'
top_param_high(path_summary, dataset_combination, parameter='length')
top_param_low(path_summary, dataset_combination, parameter='length')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='gc')
top_param_low(path_summary, dataset_combination, parameter='gc')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='mean')
top_param_low(path_summary, dataset_combination, parameter='mean')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='sd')
top_param_low(path_summary, dataset_combination, parameter='sd')
```


## NG v2 & 1M v2
```{r}
dataset_combination ='ng_vs_v2_1m'
top_param_high(path_summary, dataset_combination, parameter='length')
top_param_low(path_summary, dataset_combination, parameter='length')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='gc')
top_param_low(path_summary, dataset_combination, parameter='gc')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='mean')
top_param_low(path_summary, dataset_combination, parameter='mean')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='sd')
top_param_low(path_summary, dataset_combination, parameter='sd')
```


## STEMI v3 & 1M v3
```{r}
dataset_combination ='stemi_v3_vs_v3_1m'
top_param_high(path_summary, dataset_combination, parameter='length')
top_param_low(path_summary, dataset_combination, parameter='length')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='gc')
top_param_low(path_summary, dataset_combination, parameter='gc')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='mean')
top_param_low(path_summary, dataset_combination, parameter='mean')
```

```{r}
top_param_high(path_summary, dataset_combination, parameter='sd')
top_param_low(path_summary, dataset_combination, parameter='sd')
```








